Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-08-02 sections/results.tex
explained the result
minor changes

\textbf{Model Effectiveness Results:} From 318 samples, the comment sets from manual assessment were 85, 111, and 122 for useless set (\texttt{YES} = 0), unclear sets (\texttt{YES} = 1 or 2), and useful set (\texttt{YES} = 3), respectively. The precision and Recall of the models were 0.701 and 0.787 for useful model and 0.648 and 0.824 for useless model.

@@

%%Interpret: comments & model%%%%
Corresponding to the precision and recall values, the figure shows that the majority of comments drawn in green area are comments from the useful set, and very few comments of useless set drawn in this area.
Similarly, majority of comments drawn in the red area are comments from the useless set.
It also shows that the similarity and dissimilarity values of comments in each set are not different from other comments in the same set.
Most comments from the useful set (\texttt{YES} = 3) adhere in the top left of the graph
while those from the useless set (\texttt{YES} = 0) adhere in the bottom right of the graph.
However, the unclear set still spread out over the graph.
Therefore, we cannot determine relationship between their similarity values.

There is an overlap section as shown in Fig. \ref{fig:scatter}.
This is a conflict results between our two models where a comment received true outcome from both classification models.  
This is phenomenon can occur since similarity and dissimilarity values of each group are vague and both  models tend to maximize coverage of classification.
However, from the results in Table \ref{tb:classify_number}, only three comments were selected by both models (overlap). This is very small error for our models.
Excluding the overlap classification result, we can calculate precision and recall as described in Table \ref{tb:classify_number}. Furthermore, there are 12 useless comments (14\%) and 21 useful comments (17\%) still are undetermined (drawn in white area). These comments were not satisfied our models. This suggests us that other indicators are needed to investigate for usefulness classification.

@@

According to the results, we can answer RQ1 that \emph{using semantic similarity values as indicators, our approach successfully classify comment usefulness with precision of 0.6 and recall of 0.7 approximately and this is better than random  classification models as twice.}

@@

\textbf{Assurance:} In Table \ref{tb:classify_number}, there are 88\% of useful class have comments with \texttt{YES} = 2 and 3 voting scores. The classification of useless class also have similar proportion i.e. having high number of comment with \texttt{YES} = 0 and 1 voting scores. We conjecture that the unclear comments with \texttt{YES} = 2 might actually be useful comments and comments with \texttt{YES} = 1 might actually be useless. The unclear result could be from error of manual assessment caused by human.
To verify this conjecture, we asked practitioners to re-examine the unclear comments.
We found that 17\% of these 66 comments became unclear because of human error.
%This shows that our model \thai{what can we say about this model?}

>>>>

\textbf{Model Effectiveness Results:} From 318 samples, the comment sets from manual assessment were 85, 111, and 122 for useless set (\texttt{YES} = 0), unclear sets (\texttt{YES} = 1 or 2), and useful set (\texttt{YES} = 3), respectively. The precision and recall of the models were 0.701 and 0.787 for useful model and 0.648 and 0.824 for useless model.

@@

%%Interpret: comments & model%%%%
Corresponding to the precision and recall values, the figure shows that the majority of comments drawn in green area are comments from the useful set, and very few comments from useless set drawn in this area.
Similarly, majority of comments drawn in the red area are comments from the useless set.
It also shows that the similarity and dissimilarity values of comments in each set are not different from other comments in the same set.
Most comments from the useful set (\texttt{YES} = 3) adhere in the top left of the graph
while those from the useless set (\texttt{YES} = 0) adhere in the bottom right of the graph.
However, the unclear set still spread out over the graph.
Therefore, we cannot determine relationship between their similarity values.

There is an overlap section as shown in Fig. \ref{fig:scatter}.
This is a conflict results between our two models where a comment received true outcome from both classification models.  
This is phenomenon can occur since similarity and dissimilarity values of each group are vague and both  models tend to maximize coverage of classification.
However, from the results in Table \ref{tb:classify_number}, only three comments were selected by both models (overlap).
This means that the erroneous overlapping section is relatively small.
Excluding the overlaping classification results, we can calculate precision and recall as described in Table \ref{tb:classify_number}. Furthermore, there are 12 useless comments (14\%) and 21 useful comments (17\%) still are undetermined (drawn in white area). These comments were not satisfied our models. This suggests us that other indicators are needed to investigate for usefulness classification.

@@

According to the results, we can answer RQ1 that \emph{using semantic similarity values as indicators, our approach can successfully classify comment usefulness with precision of 0.64 and recall of 0.75 approximately, which is significantly better than a random  classifier.}

@@

\textbf{Assurance:} In Table \ref{tb:classify_number}, there are 88\% of useful class have comments with \texttt{YES} = 2 and 3 voting scores. The classification of useless class also have similar proportion i.e. having high number of comment with \texttt{YES} = 0 and 1 voting scores. We conjecture that the unclear comments with \texttt{YES} = 2 might actually be useful comments and comments with \texttt{YES} = 1 might actually be useless. The unclear result could be from error of manual assessment caused by human.
To verify this conjecture, we asked practitioners to re-examine the unclear comments.
We found that 17\% of these 66 comments became unclear because of human error.
This shows that some unclear comments are actually useful or useless, thus giving our model more confidence.
%This shows that our model \thai{what can we say about this model?}
